Implicit Neural Representation for Potential Field Geophysics

### 2023-09-21 discussion.tex
Add chapter labels and progress discussion

One of the challenges identified in \cref{paper1} was the need for large extents of suitable training data.
During the initiation of cref{paper2}, a large amount of geologically varied synthetic training data was released as \emph{the Noddyverse} \parencite{jessellNoddyverseMassiveData2022}.

@@

>>>>

One of the challenges identified in cref{paper1} was the need for large extents of suitable training data.
During the initiation of cref{paper2}, a large amount of geologically varied synthetic training data was released as \emph{the Noddyverse} \parencite{jessellNoddyverseMassiveData2022}.

@@

\section{Informed Neural Networks}
Cref{paper3} introduced to the thesis the concept of physics informed neural networks, however the .
The mechanism of informing a network is the design a criterion to impose a specific condition, which matches \emph{a priori} property of the output.
Indeed, we can extend the concept of informing a network to the use of generative adversarial networks in cref{paper1}.
A criterion is calculated, in this case \emph{discriminator loss}, using a classification network preconditioned to arbitrarily identify images as `realistic' or `not realistic'.
Using bespoke or learnt criterions greatly assists with learning high quality models, and assists with the paucity of ground truth samples in geoscience.
